High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-05-05 notebooks/poc.qmd
more work on moons for poc

```{julia}
# M = ECCCo.ConformalModel(mach.model, mach.fitresult)
# factual_label =  levels(labels)[2]
# x_factual = reshape(X[:,rand(findall(predict_label(M, counterfactual_data).==factual_label))],input_dim,1)
# target =  levels(labels)[1]
# factual = predict_label(M, counterfactual_data, x_factual)[1]

# generator_dict = Dict(
#     :wachter => WachterGenerator(),
#     :revise => REVISEGenerator(),
#     :greedy => GreedyGenerator(),
#     :eccco => ECCCoGenerator(),
# )

# ces = []
# plts = []
# for (name, generator) in generator_dict
#     ce = generate_counterfactual(
#         x_factual, target, counterfactual_data, M, generator;
#         initialization=:identity, 
#         converge_when=:generator_conditions,
#     )
#     plt = Plots.plot(ce, title=name)
#     push!(plts, plt)
#     push!(ces, ce)
# end
# display(Plots.plot(plts...))
```

>>>>

```{julia}
Random.seed!(1234)

λ₁ = 0.1
λ₂ = 0.5
λ₃ = 0.5
Λ = [λ₁, λ₂, λ₃]

M = ECCCo.ConformalModel(mach.model, mach.fitresult)
factual_label =  levels(labels)[1]
x_factual = reshape(X[:,rand(findall(predict_label(M, counterfactual_data).==factual_label))],input_dim,1)
target =  levels(labels)[2]
factual = predict_label(M, counterfactual_data, x_factual)[1]
γ = 0.5

generator_dict = OrderedDict(
    "Wachter (γ=$γ)" => WachterGenerator(λ = λ₁),
    "Schut" => GreedyGenerator(λ = λ₁),
    "REVISE" => REVISEGenerator(λ = λ₁),
    "ECCCo" => ECCCoGenerator(λ = Λ),
)

ces = Dict{Any,Any}()
plts = []
for (name, generator) in generator_dict
    conv_when = name == "Wachter (γ=$γ)" ? :decision_threshold : :generator_conditions
    ce = generate_counterfactual(
        x_factual, target, counterfactual_data, M, generator;
        initialization=:identity, 
        converge_when=conv_when,
        decision_threshold=γ,
    )
    plt = Plots.plot(ce, title=name, alpha=0.2, cbar=false, axis=nothing)
    if name == "ECCCo"
        _X = distance_from_energy(ce, return_conditionals=true)
        Plots.scatter!(
            _X[1,:],_X[2,:], color=:purple, shape=:star5, 
            ms=10, label="x̂|$target", alpha=0.5
        )
    end
    push!(plts, plt)
    ces[name] = ce
end
plt = Plots.plot(plts..., size=(500,520))
display(plt)
savefig(plt, joinpath(output_images_path, "poc.png"))
```

```{julia}
ce = ces["ECCCo"]
```
